### 2016-04-30 writing/latex/abstracteng.tex
tidy up a bit

A permutation is an arrangement of \(n\) objects.
Two mesh patterns are coincident if they are avoided by the same set of
permutations. In this thesis, the author provides sufficient conditions for
coincidence among mesh patterns, whilst also avoiding a longer classical
pattern. These conditions, along with two special cases are used to completely
classify coincidence amongst families containing a mesh pattern of length 2
and a classical pattern of length 3. The author then goes on to completely
classify Wilf-equivalence amongst mesh patterns of length 2 when we avoid the
classical pattern 231.

>>>>

A permutation is an arrangement of \(n\) objects.
Avoidance classes of classical permutation patterns
capture many interesting properties, such as
stack-sortability, and have links to many different combinatorial objects.
Mesh patterns are an extension of classical patterns that allow additional
restrictions to be placed on occurrences of the pattern.
Two mesh patterns are coincident if they are avoided by the same set of
permutations. In this thesis, the author provides sufficient conditions for
coincidence among mesh patterns, whilst also avoiding a longer classical
pattern. These conditions, along with two special cases are used to completely
classify coincidence amongst families containing a mesh pattern of length 2
and a classical pattern of length 3. Two patterns are Wilf-equivalent if they
have the same number of avoiders at every length, the author completely
Wilf-classifies mesh patterns of length 2 when avoiding the classical pattern 231.
% Finally we attempt to show some non-trivial Wilf-equivalences between avoiders
% of sets of the form \(231,m_1\) and \(231,m_2\)

### 2016-04-30 writing/latex/code.tex
tidy up a bit

\chapter{Code}\label{cha:code}
You can put code in your document using the listings package, which is
loaded by default in \path{custom.tex}.  Be aware that the listings
package does not put code in your document if you are in draft mode
unless you set the \texttt{forcegraphics} option.

There is an example java (Listing~\ref{src:Data_Bus.java}) and XML
file (Listing~\ref{src:AndroidManifest.xml}).  Thanks to the
\texttt{url} package, you can typeset OSX and unix paths like this:
\path{/afs/rnd.ru.is/project/thesis-template}.  Windows paths:
\path{C:\windows\temp\ }.  You can also typeset them using the menukey
package, but it tends to delete the last separator and has other
complications.\footnote{The menukey package has issues with biblatex,
  read \path{custom.tex} for more information.}

If you are trying to include multiple different languages, you should
go read the documentation and set these up in \path{custom.tex}.  You
will save yourself a lot of effort, especially if you have to fix
anything.

%I have put the source code in the \directory{src/} folder.
\lstinputlisting[language=Java, firstline=1,
lastline=40, caption={Data\_Bus.java: Setting up the class.},
label={src:Data_Bus.java}]{src/Data_Bus.java}

\lstinputlisting[language={[android]XML}, firstline=1, lastline=20,
caption={AndroidManifest.xml: Configuration for the Android UI.},
label={src:AndroidManifest.xml}]{src/AndroidManifest.xml}

>>>>

\chapter{Code}\label{cha:code}
% \begin{minted}[linenos, breaklines]{python}
% def boring(args=None):
%     pass
% \end{minted}
\inputminted[linenos, breaklines, frame=lines, stripall]{python}{src/main.py}
% \lstinputlisting[language=Python]{src/main.py}
% You can put code in your document using the listings package, which is
% loaded by default in \path{custom.tex}.  Be aware that the listings
% package does not put code in your document if you are in draft mode
% unless you set the \texttt{forcegraphics} option.
%
% There is an example java (Listing~\ref{src:Data_Bus.java}) and XML
% file (Listing~\ref{src:AndroidManifest.xml}).  Thanks to the
% \texttt{url} package, you can typeset OSX and unix paths like this:
% \path{/afs/rnd.ru.is/project/thesis-template}.  Windows paths:
% \path{C:\windows\temp\ }.  You can also typeset them using the menukey
% package, but it tends to delete the last separator and has other
% complications.\footnote{The menukey package has issues with biblatex,
%   read \path{custom.tex} for more information.}
%
% If you are trying to include multiple different languages, you should
% go read the documentation and set these up in \path{custom.tex}.  You
% will save yourself a lot of effort, especially if you have to fix
% anything.
%
% %I have put the source code in the \directory{src/} folder.
% \lstinputlisting[language=Java, firstline=1,
% lastline=40, caption={Data\_Bus.java: Setting up the class.},
% label={src:Data_Bus.java}]{src/Data_Bus.java}
%
% \lstinputlisting[language={[android]XML}, firstline=1, lastline=20,
% caption={AndroidManifest.xml: Configuration for the Android UI.},
% label={src:AndroidManifest.xml}]{src/AndroidManifest.xml}
